The design and implementation of standards-based Grid single sign-on using federated identity

### 2009-04-17 doc/sec/papers/GRID09/paper.tex
more content; have not applied the comments yet

\begin{abstract}
Security infrastructure is one of the most challenging tasks in the developement, integration and
deployment of Grid middlewares. Even though the Grid community addresses the security issue 
through public key infrastructures (PKI) to support mutual authentication using X.509 certificates,
maintaining the X.509 credential is not that easy for non-IT specialists, and is proved to be an 
obstacle for the more widely deployment of Grid technology. Considering the identity federation 
technology is a emergingly widely used technology which can facilitate cross-domain single sign-on,
without requiring the users to maintain the X.509 credentials rather than their own institutional
accounts, we believe utilizing identity federation for Grid middlwares is a promising direction 
for Grid technology to be more widely used.
This paper describes a single sign-on infrastructure developed as part of the NorduGrid/ARC grid 
middleware. It adopts the identity federation standard (SAML), as well as Web Service standand. 
It focus on single sign-on solution on the middleware level for users to access Grids by only 
using their frequently used accounts, without being bothered to maintain X.509 credentials. 
Unlike other research which utilize identity federation on the Grid portal level, solution on
the middleware level can provide more flexibility.
Also, the performance of single sign-on solution is measured. We identify the performance limitation 
of security-related services inside this solution, and analyze the ways to avoid or improve the 
limitation. 
To our knowledge, the work described in this paper is the first evaluated implementation that utilizes 
identity federation for Grid usage on the middlware level.
\end{abstract}

@@

The current Grid community uses Grid Security Infrastructure (GSI)~\cite{IFoster98} as the de facto 
standard for authentication and transport level security, which builds on the Public Key Infrastructure
(PKI) to support authentication using X.509 certificate. Mutual authentication is required 
by GSI based Grid deployment. Mutual authentication means that Grid users have to possess X.509 
credentials. To obtain a X.509 credential, a user needs to contact the Registration Authority (RA)
which will check the user's information and approve his certificate request; afterwards,
the Certificate Authority (CA) can issue the certificate according to the approval from 
the RA. The whole process is arduous and may take some time.
Meanwhile, to maintain a X.509 certificate is also not so easy for the non-IT community to deal 
with, since users have to periodically create proxy certificates by using Grid-specific command line 
utility, such as grid-proxy-init or voms-proxy-init. Also maintaing the CAs or RAs is also not a  
easy task, especially when the community of Grid users is getting much wider.

On the other hand, users normally could already have had some frequently-used campus or institutional 
accounts/credentials such as username/password. We believe that enabling Grid users to use their home 
credentials rather than the X.509 certificate to access Grids is a promising way 
to make the Grids more easily accessible, as well as to extend the user community of Grids
to a much larger scale.

To enable users to utilize the institutional credentials to access Grid, some issues needs to be 
addressed. Firstly, the Grid middleware needs to be improved to support the authentication based on
institutional credentials instead of X.509 certificates; Secondly, in order to interoperate with
those Grid infrastructures which require X.509 certificate based mutual authentication, an approach
should be provided for obtaining X.509 certificate based on the institutional credentials; Thirdly,
the single sign-on characteristic should be provided so that users can login once and then transverse 
from Grid resources to Grid resources without being prompted to log in again at each of the resources.

The approach in the new version of ARC grid middleware is to utilize the identity federation 
standards, specifically, the Security Assertion Markup Language (SAML) specification, and Web 
Service standards, to make the Grid single sign-on be possible.

@@

The next generation of ARC components is developed by the KnowARC project~\cite{KnowARClink}, based on the functionality and capabilities of the classic ARC middleware. It aims at implementing a Web Service oriented Grid middleware which will provide higher levels of resource and user abstraction through well-defined Web Service interface~\cite{KnowARCDesignlink} in order to provide interoperability with other service-based Grid middlewares, as well as other Web Service compatible applications.

As the key part of the implementation of new ARC middleware, there is a lightweight Web Service container called Hosting Environment Daemon (HED) which provides hosting for various services at application level, as well as a number of modules to support flexible, interoperable, and efficient communication mechanism for building SOAP based Web Services. The whole design of the HED is built around the idea of flexibility and modularity.

@@

\begin{figure}
\includegraphics[width=0.9\columnwidth]{HED.pdf}
\caption{The example of Host Environment Daemon deployed with A-REX and File services}
\label{fig:HED}
\end{figure}
HED contains a framework for implementing and enforcing authentication and authorization. Each MCC or Service has a common interface for implementing various authentication and authorization functionality. Each functionality can be implemented as a pluggable and configurable component (plug-ins) called SecHandler, which is implemented as a C++ class and provides a method for processing message that travels through MCC or Service. Each MCC or Service is usually configured with two queues of SecHandler -- one for the incoming message and one for the outgoing message respectively. In Figure \ref{fig:HED}, the ``AuthZ'' and ``AuthN'' sub-modules inside MCCs and Services are examples of SecHandler.

@@

%-------------------------------------------------------------------------
\section{Performace Evaluation}
\label{sec:perfeval}
The following section evaluate the performance of the

@@

Figure \ref{fig:HED2Axis_thread10} and Figure \ref{fig:HED2Axis_thread40} are the results of 
performance comparison. 
Two types of experiments are shown: session reused, session no-reused.
``Session reused'' means all of the SOAP invocations on each client share the same session 
(tcp connection); while ``Session no-reused'' means each invocation launches a new session.

@@

For ``Session no-reused'' experiments, the average response time in HED is almost the same as
the value in Axis2/C, in both cases of client number is 10 (the value is 15ms) and 40 (the value
 is 53ms) correspondingly. On the other hand the throughput in HED is also the same as the value 
in Axis2/C, in both cases of client number is 10 and 40. One interesting obersabation is that the 
throughput is close to a fixed value (around 500 request/s) for both HED and Axis2/C in both 
cases of client number, when the duration value becomes bigger. Also, in case of client number is
40, the throughput from ``Session reused'' experiments also is close to the same fixed value.
We speculate that, with a relatively big value of client number, no matter the session is reused or
not, the throughput is becoming a fixed value which can be explained as the SOAP processing capability
of the SOAP implementation. In this case, we can believe that HED has the similar performance 
capability as Axis2/C.

@@

Figure \ref{fig:SAML2SSO_thread1} depicts the average response time and throughputs for one client 
running against the service. Since the success of authentication from IdP can be regarded as 
valid for the whole session between client and service, the client with ``Session reused'' 
need to accomplish the SAML2SSO profile only once for all SOAP invocations on this client, 
while the client with ``Session no-reused'' will need to accomplish this profile once per 
SOAP invocation.

The average response time of ``Session no-reused'' experiments changes little with the execution 
duration, and the value is about 730ms; while the throughput is around 82 requests per minutes.
Considering that the average response time in case of 
``Session no-reused'' and pure SOAP invocation is around 15ms when client number is 10 (see section
\ref{sec:perhedandaxis}), not demostrated in section \ref{sec:perhedandaxis}, the same value applies 
when client number is only 1, therefore we can calculate that the consumption of time for 
SAML2SSO profile is about 98\% of the whole SOAP invocation with SAML2SSO profile integrated.
Deeper investigation about recording the time of each step of SAML2SSO profile supports the above
obersavation. In order to improve the performance of SAML2SSO profile, optimizing the process between
client and IdP is the correct direction, and probably one of the easiest way is to enhance the 
hardware configuration.

@@

%-------------------------------------------------------------------------
\section{Related Work}
\label{sec:relatedwork}
Similar work that integrates Shibboleth and Grid middleware does exist. GridShib~\cite{VWelch05,TBarton06} uses Shibboleth to get entity's attribute for the authorization of services developed in Globus Tookit. Unlike the work described in this paper, the GridShib does not use Shibboleth's native login handlers for authentication to Shibboleth IdP, instead, a new login handler specific for X.509 based authentication is developed for the Shibboleth IdP, and a credential service is developed for acting as an online-CA, authenticating the user, and issuing short-lived X.509 credential. Moreover, this paper provides a single sign-on solution for the user with community credentials authenticating to Grid services by directly using SAML2.0 SSO profile.

SWITCH (The Swiss Education and Research Network) short-lived credential service (SLCS)~\cite{switchslcslink} provides a SLCS service and a client. The advantage of our work comparing to the SWTCH's solution is that the SLCS service and client are based on Web Services, so that they can be implemented in any Web Service container while keeping interoperability.

In terms of delegation, apart from the credential delegation mechanism of GSI~\cite{IFoster98,VWelch04}, several authors~\cite{MAhsant04} propose a delegation protocol based on the WS-Trust~\cite{WSTrustlink} in order to provide a standard and interoperable protocol for the delegation in Grids. WS-Trust will also be adopted by the ARC middleware to express the specifications required to define delegation protocol in a standard way. Gridsite project implements a X.509 credential delegation solution~\cite{GridSitelink} based on the Web Service, with which ARC delegation client can be made easily interoperable.

%-------------------------------------------------------------------------
\section{Conclusion And Future Work}
\label{sec:conclusion}
In this paper we presented the solution built into the ARC Grid middleware, aiming towards the cross-middle-ware authentication and single sign-on. The goal of our work is to develop an interoperable and accessible single sign-on solution to be used for a VO scenario in production Grids, where users can easily authenticate against the Grids with any of their credentials (not only X.509) from anywhere, and move inside Grid middleware infrastructure and even across heterogeneous Grids  boundaries, without re-authentication within a reasonable period. In order to do so, we implemented some standards based Web Services (including the SLCS service, the X.509 credential delegation service, and the SAML Token delegation service), as well as the user agent and the Service Provider in the context of the SAML2 SSO profile.

It must be noted that due to the standard specifications utilized (SAML and WS-Security) which are independent from any particular middleware, the WS clients and Web/Grid Services developed within the ARC middleware can interoperate with WS clients and Web/Grid Services developed as part of some other middlewares in a standardized way.

Though only authentication issue is discussed in this paper, as the future work, we will implement a solution for cross-middleware attribute-based authorization by using the standard specifications such as SAML.

@@

\bibitem{IFoster01}
I. Foster, C. Kesselman, S. Tuecke. The anatomy of the Grid: Enabling scalable virtual organizations, International Journal of Supercomputer Applications, 15(3), 200-222 (2001)

@@

@@

\bibitem{VWelch05}
V. Welch, T. Barton, K. Keahey and F. Siebenlist. Attributes, Anonymity, and Access: Shibboleth and Globus Integration to Facilitate Grid Collaboration. 4th Annual PKI R\&D Workshop, 2005.

\bibitem{TBarton06}
T. Barton et al. Identity Federation and Attribute-based Authorization through the Globus Toolkit, Shibboleth, Gridshib, and MyProxy. 5th Annual PKI R\&D Workshop, 2006.

@@

\bibitem{VWelch04}
V. Welch et al. X.509 proxy certificate for dynamic delegation, Proceeding of the 3rd Annual KI R\&D Workshop, 2004.

\bibitem{MAhsant04}
M. Ahsant, J. Basney, and O. Mulmo. Grid Delegation Protocol, UK Workshop on Grid Security Experiences, Oxford. 2004.

@@

>>>>

\begin{abstract}
Security infrastructure is one of the most challenging tasks in the developement, integration and
deployment of Grid middlewares. Even though the Grid community addresses the security issue 
through public key infrastructures (PKI) to support mutual authentication using X.509 certificates,
maintaining the X.509 credential is not that easy for non-IT specialists, and is proved to be an 
obstacle for the more widely deployment of Grid technology. Considering the identity federation 
technology is a emergingly widely used technology which can facilitate cross-domain single sign-on,
without requiring the users to maintain the X.509 credentials rather than their own institutional
accounts, we believe utilizing identity federation for Grid middlwares is a promising direction 
for Grid technology to be more widely used.
This paper describes a single sign-on infrastructure developed as part of the NorduGrid/ARC grid 
middleware. It adopts the identity federation standard (SAML), as well as Web Service standand. 
It focus on single sign-on solution on the middleware level for users to access Grids by only 
using their frequently used accounts, without being bothered to maintain X.509 credentials. 
Unlike other research which utilize identity federation on the Grid portal level, solution on
the middleware level can provide more flexibility.
Also, the performance of single sign-on solution is measured. We identify the performance limitation 
of security-related services inside this solution, and analyze the ways to avoid the limitation.
To our knowledge, the work described in this paper is the first evaluated implementation that utilizes 
identity federation for Grid usage on the middlware level.
\end{abstract}

@@

The current Grid community uses Grid Security Infrastructure (GSI)~\cite{IFoster98} as the de facto 
standard for authentication and transport level security, which builds on the Public Key Infrastructure
(PKI) to support authentication using X.509 certificate. Mutual authentication is required 
by GSI based Grid deployment. Mutual authentication means that Grid users have to possess X.509 
credentials. To obtain a X.509 credential, a user needs to contact the Registration Authority (RA)
which will check the user's information and approve his certificate request; afterwards,
the Certificate Authority (CA) can issue the certificate according to the approval from 
the RA. The whole process is arduous and may take some time.
Meanwhile, to maintain a X.509 certificate is also not so easy for the non-IT community to deal 
with, since users have to periodically create proxy certificates by using Grid-specific command line 
utilities, such as grid-proxy-init or voms-proxy-init. Also maintaing the CAs or RAs is not a  
easy task, especially when the community of Grid users is getting much wider.

On the other hand, users normally could already have had some frequently-used campus or institutional 
accounts/credentials such as username/password. We believe that enabling Grid users to use their institutional 
credentials rather than the X.509 certificate to access Grids is a promising way 
to make the Grids more easily accessible, as well as to extend the user community of Grids
to a much larger scale.

To enable users to utilize the institutional credentials to access Grid, some issues needs to be 
addressed. Firstly, the Grid middleware needs to be improved to support the authentication based on
institutional credentials instead of X.509 certificates; Secondly, in order to interoperate with
those Grid infrastructures which require X.509 certificate based mutual authentication, an approach
should be provided for obtaining X.509 certificate based on the institutional credentials; Thirdly,
the single sign-on characteristic should be provided so that users can authenticate once and then transverse 
from Grid resources to Grid resources without being prompted to authenticate again at each of the resources.

The approach in the new version of ARC grid middleware is to utilize the identity federation 
standards, specifically, the Security Assertion Markup Language (SAML) specification, and Web 
Service standards, to facilitate the Grid single sign-on.

@@

The development version of ARC components is developed by the KnowARC project~\cite{KnowARClink}, 
based on the functionality of the current production ARC middleware. It aims at 
implementing a Web Service oriented Grid middleware which will provide higher levels of 
resource and user abstraction through well-defined Web Service interface~\cite{KnowARCDesignlink} 
in order to provide interoperability with other Web Service oriented Grid middlewares, as well as 
other Web Service compatible applications.

As the key part of the implementation of new ARC middleware, there is a lightweight Web 
Service container called Hosting Environment Daemon (HED) which provides hosting environment 
for various services at application level, as well as a number of modules to support flexible, 
interoperable, and efficient communication mechanism for building SOAP based Web Services. 
The design of the HED is built around the idea of flexibility and modularity,
such that the application service developers can simply concentrate on the application 
level Web Service implementation by only using the core minimum amount of components. It 
also simplifies work on the middleware level, e.g. making possible to implement another 
communication protocol or authentication mechanism. A system administrator can easily 
configure and deploy the middleware and application for different kinds of requirements 
without having to know much about the implementation.

@@

Dotted line in Figure \ref{fig:HED} shows an alternative path for the information 
to propagate among MCCs. A service administrator can configure the MCCs according to the 
interoperability requirements with the other part. For instance, the configuration marked 
with the dotted line is compatible with the WSE (Web Services Enhancement for .NET) SOAP 
message mechanism (see WSE’s SoapSender and SoapReceiver)~\cite{WSElink}. Another configuration 
could be SOAP over HTTPG (HTTP over GSI) which is needed to interoperate with services 
like the Storage Resource Manager (SRM)~\cite{A.Shoshan03} service. This shows the 
flexibility of HED in terms of protocols support.

\begin{figure}
\includegraphics[width=0.9\columnwidth]{HED.pdf}
\caption{The example of Host Environment Daemon deployed with A-REX and File services}
\label{fig:HED}
\end{figure}

HED contains a flexible security framework for implementing and enforcing security 
related functionality, such as authentication and authorization. 
Each security related functionality can be implemented as a pluggable and configurable 
component (plug-ins) called SecHandler. Each MCC or Service is usually configured with 
two queues of SecHandler -- one for the incoming message and one for the outgoing message 
respectively. In Figure \ref{fig:HED}, the ``AuthZ'' and ``AuthN'' sub-modules inside 
MCCs and Services are examples of SecHandler.

@@

%-------------------------------------------------------------------------
\section{Performace Evaluation}
\label{sec:perfeval}
The following sections evaluate the performance of the HED versus Axis2/C, as 
well as the performance about the SAML2SSO profile, short-lived credential
service, and delegation service.

@@

Figure \ref{fig:HED2Axis_thread10} and Figure \ref{fig:HED2Axis_thread40} are the results of 
performance comparison. 
Two types of experiments are shown: session reused, session non-reused.
``Session reused'' means all of the SOAP invocations on each client share the same session 
(tcp connection); while ``Session non-reused'' means each invocation launches a new session.

@@

For ``Session non-reused'' experiments, the average response time in HED is almost the same as
the value in Axis2/C, in both cases of client number is 10 (the value is 15ms) and 40 (the value
 is 53ms) correspondingly. On the other hand the throughput in HED is also the same as the value 
in Axis2/C, in both cases of client number is 10 and 40. One interesting obersabation is that the 
throughput is close to a fixed value (around 500 request/s) for both HED and Axis2/C in both 
cases of client number, when the duration value becomes bigger. Also, in case of client number is
40, the throughput from ``Session reused'' experiments also is close to the same fixed value.
We speculate that, with a relatively big value of client number, no matter the session is reused or
not, the throughput is becoming a fixed value which can be explained as the SOAP processing capability
of the SOAP implementation. In this case, we can believe that HED has the similar performance 
capability as Axis2/C.

@@

Figure \ref{fig:SAML2SSO_thread1} depicts the average response time and throughputs for one client 
running against the service. Since the success of authentication from IdP can be regarded as 
valid for the whole session between client and service, the client with ``Session reused'' 
need to accomplish the SAML2SSO profile only once for all SOAP invocations on this client, 
while the client with ``Session non-reused'' will need to accomplish this profile once per 
SOAP invocation.

The average response time of ``Session non-reused'' experiments changes little with the execution 
duration, and the value is about 730ms; while the throughput is around 82 requests per minutes.
Considering that the average response time in case of 
``Session non-reused'' and pure SOAP invocation is around 15ms when client number is 10 (see section
\ref{sec:perhedandaxis}), not demostrated in section \ref{sec:perhedandaxis}, the same value applies 
when client number is only 1, therefore we can calculate that the consumption of time for 
SAML2SSO profile is about 98\% of the whole SOAP invocation with SAML2SSO profile integrated.
Deeper investigation about recording the time of each step of SAML2SSO profile supports the above
obersavation. In order to improve the performance of SAML2SSO profile, optimizing the process between
client and IdP is the correct direction, and probably one of the easiest way is to enhance the 
hardware configuration.

@@

%-------------------------------------------------------------------------
\section{Related Work}
\label{sec:relatedwork}
There are other researches that utilize Shibboleth for protecting usage of Grid resources. 
The work in ~\cite{J.Watt06} uses Shibboleth to protect a GridSphere portal and then 
indirectly protect Grid services which are deployed in this GridSphere protal. Another 
work in ~\cite{R.O.Sinnott06} also uses Shibboleth to protect Grid portal, moreover, it 
maintains a few common used server certificates which can then be used to access Grid 
resources after users have successfully authenticated themselves at Grid protal through
Shibboleth. Unlike these two solutions that use Shibboleth to protect Grid portal, the solution
in this paper uses Shibboleth or similar standards-based identity federation to directly protect 
Grid resource/services, which provide possibility for those Grid applications that are directly
based on Grid interface (e.g., applications that invokes SOAP operations of remote Grid services),
to benefit from identity federation.

GridShib~\cite{T.Scavo07,VWelch05} provides one solution that users can use X.509 
certificate to authenticate to Shibbolth IdP, get back SAML assertion and embed it in 
the proxy certificate. The Grid service will then use this SAML assertion for access control.
Unlike the work described in this paper, GridShib still requires users to possess a X.509 
credential, rather than username/password. GridShib also provides another 
solution~\cite{TBarton06} in which a credential service (MyProxy server) is deployed together
with Shibboleth IdP for acting as an online-CA, authenticating the user through username/password
rather than X.509 certificate, and issuing short-lived X.509 credential. The second solution
is similar to the short-lived credential service in our solution, while our solution
also provides the option for users directly authenticating to Grid services via SAML2.0 SSO 
profile using their username/password.

Another short-lived credential service is also provided by ~\cite{switchslcslink}. 
The advantage of our work comparing to the work in ~\cite{switchslcslink} is that 
our SLCS service is based on Web Services standard, so that it is easier to achieve 
interoperability.

In the aspect of credential delegation, apart from the credential delegation mechanism of 
GSI~\cite{IFoster98,VWelch04}, several authors~\cite{MAhsant04} propose a delegation protocol 
based on the WS-Trust~\cite{WSTrustlink} to provide a standard and interoperable protocol 
for the delegation in Grids. WS-Trust will also be adopted by the ARC middleware to express the 
specifications required to define delegation protocol in a standard way. Gridsite project also
implements a X.509 credential delegation solution~\cite{GridSitelink} based on the Web 
Service, with which ARC delegation client can be easily made interoperate.

%-------------------------------------------------------------------------
\section{Conclusion And Future Work}
\label{sec:conclusion}
In this paper we propose a Grid single sign-on framework that can utilize users' 
federated identity instead of X.509 mutual authentication for authentication, which
we believe can make further uptake of Grid resources as well as Grid middleware by 
wider scale of users.

We implement the SAML2 SSO profile in the ARC Grid middleware, so that the Grid applications
that developed by using the application interface provided by this middleware can easily 
be switched to benefit from federated identity based authentication. 
The performance evaluation shows even though the introducing of SAML2 SSO profile causes 
much performance downgrade, this downgrade can be avoided by reusing the authentication 
result for multiple SOAP invocations.
Meanwhile, in order to be compatible with those Grid applications that require X.509 
certificate on the client side, we also implement one Web Service which can be used for 
obtaining an X.509 credential based on federated identity, and the other Web Service 
which can be used for delegating X.509 credential. We believe that the evaluated 
performance is enough for creating X.509 certificate and proxy certificate, considering that 
the certificates should have a relaively much longer lifetime comparing to the response time of 
these two services.

Although only authentication issue has been discussed in this paper, we know single
sign-in should also include the authorization issue. The SAML assertion which includes
users' attributes can be used on the serrvice side to achiece attribute-based authorization.
Therefore providing plugin on the service side to enforce access control using SAML attribute
is considered one part of the future work.

SimpleSAMLphp~\cite{simplesamllink} provides another implementation of SAML2 SSO profile, and it 
has been widely deployed around nordic countries for identity federation. Hence integrating
ARC based Grid applications with simpleSAMLphp is considered as another of future work.

@@

@@

\bibitem{WSElink}
Web Services Enhancements 2.0 Service Pack 2. http://msdn.microsoft.com/en-us/library/

\bibitem{A.Shoshan03}
A. Shoshani, A. Sim, and J. Gu, Storage Resource Managers: Essential Components for the Grid, 
Grid Resource Management: State of the Art and Future Trends, Kluwer Publishing, 2003.

@@

\bibitem{R.O.Sinnott06}
R.O. Sinnott, J. Jiang, J. Watt, and O. Ajayi. Shibboleth-based access to and 
usage of grid resources. Proceeding of 7th IEEE/ACM International Conference on 
Grid Computing, September 2006, Barcelona.

\bibitem{J.Watt06}
J. Watt, O. Ajayi, J. Jiang, J. Koetsier, R.O. Sinnott. A Shibboleth-Protected 
Privilege Management Infrastructure for e-Science Education. in proceeding of Sixth 
IEEE International Symposium on Cluster Computing and the Grid (CCGRID'06), May 2006,
Singapore.

\bibitem{T.Scavo07}
T. Scavo and V. Welch. A Grid Authorization Model for Science Gateways. International 
Workshop on Grid Computing Environments, 2007.

\bibitem{VWelch05}
V. Welch, T. Barton, K. Keahey and F. Siebenlist. Attributes, Anonymity, and 
Access: Shibboleth and Globus Integration to Facilitate Grid Collaboration. in 
proceeding of 4th Annual PKI R\&D Workshop, 2005.

\bibitem{TBarton06}
T. Barton et al. Identity Federation and Attribute-based Authorization 
through the Globus Toolkit, Shibboleth, Gridshib, and MyProxy. in proceeding 
of 5th Annual PKI R\&D Workshop, 2006.

@@

\bibitem{VWelch04}
V. Welch et al. X.509 proxy certificate for dynamic delegation. in proceeding 
of the 3rd Annual KI R\&D Workshop, 2004.

\bibitem{MAhsant04}
M. Ahsant, J. Basney, and O. Mulmo. Grid Delegation Protocol. UK Workshop on 
Grid Security Experiences, Oxford. 2004.

@@

\bibitem{simplesamllink}
http://rnd.feide.no/simplesamlphp
